---
title: "Skills Snapshot"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 7
  html_notebook: 
    fig_height: 7
    fig_width: 7
---


```{r}
require(GGally)     # Required for ggpairs
require(ggplot2)    # GGally supersets on ggplot2
require(ggpubr)

require(gridExtra)
library('datasets')

data(iris)

str(iris)
summary(iris)

p_iris <-ggpairs(data=iris, title = "The Iris Data Set", upper = list(continuous = wrap("cor", size = 2, alignPercent=0.9)), 
mapping=ggplot2::aes(color=Species), lower=list(combo=wrap("facethist",binwidth=1)))

plot_iris <- p_iris +
  theme_dark() + theme(axis.text.x = element_text(angle = 90))
  # theme(axis.text.x = element_text(angle = 45), axis.text.y = element_text(angle = 45))

# p_iris
plot_iris
```
```{r}
ggpairs(iris,upper = list(continuous = wrap('cor', method = "kendall",size=4,alignPercent=0.9)), axisLabels = "blank",ggplot2::aes(color = species),size=10) +theme(text = element_text(size=10),axis.text.x=element_text(angle=45,hjust=1,size=10)) + theme_bw()
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
```{r}

```

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
